Trajipaq_sentiment_cr

### 2023-07-30 1. Trajipaq_sentiment/2. Codes/Trajipaq_sentiment_cr.Rmd
update CSD

trajipaq <-
  trajipaq %>%
  mutate(revenu = factor(case_when( # Création de la variable "revenu".
    Q100 == 1 ~ "[0 ; 39 999]",
    Q100 == 2 ~ "[0 ; 39 999]",
    Q100 == 3 ~ "[0 ; 39 999]",
    Q100 == 4 ~ "[0 ; 39 999]",
    Q100 == 5 ~ "[40 000 ; 99 999]",
    Q100 == 6 ~ "[40 000 ; 99 999]",
    Q100 == 7 ~ "[60 000 ; 99 999]",
    Q100 == 8 ~ "[60 000 ; 99 999]",
    Q100 == 9 ~ "[80 000 ; 99 999]",
    Q100 == 10 ~ "[100 000 et plus]",
    Q100 == 11 ~ "[100 000 et plus]",
    Q100 == 12 ~ "[100 000 et plus]",
    Q100 == 98 ~ NA,
    Q100 == 99 ~ NA
  ), levels = c(
  "[0 ; 39 999]",
  "[40 000 ; 39 999]",
  "[60 000 ; 99 999]",
  "[100 000 et plus]",
  NA)))

>>>>

trajipaq <-
  trajipaq %>%
  mutate(revenu = factor(case_when( # Création de la variable "revenu".
    Q100 == 1 ~ "[0 ; 19 999]",
    Q100 == 2 ~ "[0 ; 19 999]",
    Q100 == 3 ~ "[20 000 ; 29 999]",
    Q100 == 4 ~ "[30 000 ; 39 999]",
    Q100 == 5 ~ "[40 000 ; 49 999]",
    Q100 == 6 ~ "[50 000 ; 59 999]",
    Q100 == 7 ~ "[60 000 ; 69 999]",
    Q100 == 8 ~ "[70 000 ; 79 999]",
    Q100 == 9 ~ "[80 000 ; 99 999]",
    Q100 == 10 ~ "[80 000 ; 99 999]",
    Q100 == 11 ~ "[100 000 et plus]",
    Q100 == 12 ~ "[100 000 et plus]",
    Q100 == 98 ~ NA,
    Q100 == 99 ~ NA
  ), levels = c(
  "[0 ; 19 999]",
  "[20 000 ; 29 999]",
  "[30 000 ; 39 999]",
  "[40 000 ; 49 999]",
  "[50 000 ; 59 999]",
  "[60 000 ; 69 999]",
  "[70 000 ; 79 999]",
  "[80 000 ; 99 999]",
  "[100 000 et plus]",
  NA)))
